---
title: "Final Blog"
author: "Yue Wang"
date: '2022-06-08'
output:
  word_document: default
  pdf_document: default
---

# R Markdown

## Catalog
  Introduction \
  Research Interests \
  Load Packages \
  Data Description \
  Data Analysis \
    1. Sentiment Analysis \
    2. Word Cloud \
    3. Topic Model \
    4. Tf_idf \
    5. Bigram & Network Graph \
  Conclusion

## Introduction

For the final project, I choosed articles of Peter Hessler as my research dataset.
Peter Hessler is a staff writer at The New Yorker. He is the magazine's correspondent in China from 2000 to 2007. He was based in Egypy from 2011 to 2016. Most of the subjects of his articles are about these two countries, but also include a small-town druggist in Colorado.

I was reading his latest post when the final assignment requests released, and his ties to China and Colorado led me to choose his post as the dataset.

## Research Interests

Peter Hessler is the winner of an American Society of Magazine Editors Award, and he's also famous in China. Many people like him because his writing is very detailed, recording things we know in a different way. However, lots of people hate him and think he describes things negatively.

My main interest is "Is it true?". Luckily, we have learned sensitiment analysis and the machine will tell us the answer. I also did wordcloud, topicmodel, tf-idf, bigram and network graph to further study what his articles covers.

## Load Packages

```{r results='hide'}
#Load Packages
library(tidyverse)
library(tidytext)
library(RColorBrewer)
library(wordcloud)
library(rvest)
library(igraph)
library(ggraph)
library(topicmodels)
```

## Data Description

As a contributor, Peter has his own page at The New Yorker website. You can access all his articles from 2000 to last month through the website. I picked 60 articles from May 2008 to May 2022, which is a large dataset given that each of his articles is usually greater than 5,000 words.

I used SelectorGadget to scrape the body of the articles from the webpage, add title, the country involved, and article number information for tracking. Then, I used bind_rows to put data together.

For further research, it might be possible to scrape his writing time to examine whether his writing style has changed over time, but that is not included in my current study.

```{r read in data}
# Example
# I've provided grab and add data sample here, hiding most of the code to avoid redundant reporting

# 1.A Teacher in China Learns the Limits of Free Expression
ph1 <- read_html("https://www.newyorker.com/magazine/2022/05/16/a-teacher-in-china-learns-the-limits-of-free-expression")

ph1_text <- ph1 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "1") %>% 
  mutate( country = "China") %>% 
  mutate( title = "A Teacher in China Learns the Limits of Free Expression")

```

```{r include=FALSE}
# 2.China's Reform Generation Adapts to Life in the Middle Class
ph2 <- read_html("https://www.newyorker.com/magazine/2022/01/03/chinas-reform-generation-adapts-to-life-in-the-middle-class")

ph2_text <- ph2 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "2") %>% 
  mutate( country = "China") %>% 
  mutate( title = "China's Reform Generation Adapts to Life in the Middle Class")

# 3. Learning to Ski in a Country of Beginners
ph3 <- read_html("https://www.newyorker.com/magazine/2021/06/21/learning-to-ski-in-a-country-of-beginners")

ph3_text <- ph3 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "3") %>% 
  mutate( country = "China") %>% 
  mutate( title = "Learning to Ski in a Country of Beginners")

ph3_text

# 4. The Rise of Made-in-China Diplomacy
ph4 <- read_html("https://www.newyorker.com/magazine/2021/03/15/the-rise-of-made-in-china-diplomacy")

ph4_text <- ph4 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "4") %>% 
  mutate( country = "China") %>% 
  mutate( title = "The Rise of Made-in-China Diplomacy")

ph4_text

# 5. Nine Days in Wuhan, the Ground Zero of the Coronavirus Pandemic
ph5 <- read_html("https://www.newyorker.com/magazine/2020/10/12/nine-days-in-wuhan-the-ground-zero-of-the-coronavirus-pandemic")

ph5_text <- ph5 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "5") %>% 
  mutate( country = "China") %>% 
  mutate( title = "Nine Days in Wuhan, the Ground Zero of the Coronavirus Pandemic")

ph5_text

# 6. Chinese Citizens Are Already Receiving a Coronavirus Vaccine
ph6 <- read_html("https://www.newyorker.com/news/news-desk/the-november-surprise-of-chinas-coronavirus-vaccine")

ph6_text <- ph6 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "6") %>% 
  mutate( country = "China") %>% 
  mutate( title = "Chinese Citizens Are Already Receiving a Coronavirus Vaccine")

ph6_text

# 7. How China Controlled the Coronavirus
ph7 <- read_html("https://www.newyorker.com/magazine/2020/08/17/how-china-controlled-the-coronavirus")

ph7_text <- ph7 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "7") %>% 
  mutate( country = "China") %>% 
  mutate( title = "How China Controlled the Coronavirus")

ph7_text

# 8. Life on Lockdown in China
ph8 <- read_html("https://www.newyorker.com/magazine/2020/03/30/life-on-lockdown-in-china")

ph8_text <- ph8 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "8") %>% 
  mutate( country = "China") %>% 
  mutate( title = "Life on Lockdown in China")

ph8_text

# 9. The Peace Corps Breaks Ties with China
ph9 <- read_html("https://www.newyorker.com/magazine/2020/03/16/the-peace-corps-breaks-ties-with-china")

ph9_text <- ph9 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "9") %>% 
  mutate( country = "China") %>% 
  mutate( title = "The Peace Corps Breaks Ties with China")

ph9_text

# 10. China's L.B.J. Cliffhanger!
ph10 <- read_html("https://www.newyorker.com/magazine/2020/02/10/chinas-lbj-cliffhanger")

ph10_text <- ph10 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "10") %>% 
  mutate( country = "China") %>% 
  mutate( title = "China's L.B.J. Cliffhanger!")

ph10_text

# 11. Mohamed Morsi, Who Brought the Muslim Brotherhood to the Egyptian Presidency
ph11 <- read_html("https://www.newyorker.com/news/news-desk/mohamed-morsi-who-brought-the-muslim-brotherhood-to-the-egyptian-presidency")

ph11_text <- ph11 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "11") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "Mohamed Morsi")

ph11_text

#12. My House in Cairo
ph12 <- read_html("https://www.newyorker.com/culture/personal-history/my-house-in-cairo")

ph12_text <- ph12 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "12") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "My House in Cairo")

ph12_text

# 13. The Refugee and the Thief
ph13 <- read_html("https://www.newyorker.com/magazine/2019/04/01/egyptian-refugee")

ph13_text <- ph13 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "13") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "The Refugee and the Thief")

ph13_text

# 14. Cairo: A Type of Love Story
ph14 <- read_html("https://www.newyorker.com/magazine/2018/05/07/cairo-a-type-of-love-story")

ph14_text <- ph14 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "14") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "Cairo: A Type of Love Story")

ph14_text

# 15. How Trump Is Transforming Rural America
ph15 <- read_html("https://www.newyorker.com/magazine/2017/07/24/how-trump-is-transforming-rural-america")

ph15_text <- ph15 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "15") %>% 
  mutate( country = "U.S.") %>% 
  mutate( title = "How Trump Is Transforming Rural America")

ph15_text

# 16. Learning Arabic from Egypt's Revolution 
ph16 <- read_html("https://www.newyorker.com/magazine/2017/04/17/learning-arabic-from-egypts-revolution")

ph16_text <- ph16 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "16") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "Learning Arabic from Egypt's Revolution")

ph16_text

# 17. Egypt's Failed Revolution
ph17 <- read_html("https://www.newyorker.com/magazine/2017/01/02/egypts-failed-revolution")

ph17_text <- ph17 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "17") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "Egypt's Failed Revolution")

ph17_text

# 18. Making Peace with Trump's Revolutionaries
ph18 <- read_html("https://www.newyorker.com/news/news-desk/making-peace-with-trumps-revolutionaries")

ph18_text <- ph18 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "18") %>% 
  mutate( country = "U.S.") %>% 
  mutate( title = "Making Peace with Trump's Revolutionaries")

ph18_text

# 19. Living-Room Democracy
ph19 <- read_html("https://www.newyorker.com/magazine/2016/03/07/egypts-singular-stay-at-home-campaigns")

ph19_text <- ph19 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "19") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "Living-Room Democracy")

ph19_text

# 20. Invisible Bridges: Life Along the Chinese-Russian Border
ph20 <- read_html("https://www.newyorker.com/culture/photo-booth/invisible-bridges-life-along-the-chinese-russian-border")

ph20_text <- ph20 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "20") %>% 
  mutate( country = "China") %>% 
  mutate( title = "Invisible Bridges: Life Along the Chinese-Russian Border")

ph20_text

# 21. Ryan Hall, America's Fastest Marathoner, Slows Down
ph21 <- read_html("https://www.newyorker.com/sports/sporting-scene/ryan-hall-americas-fastest-marathoner-slows-down")

ph21_text <- ph21 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "21") %>% 
  mutate( country = "U.S.") %>% 
  mutate( title = "Ryan Hall, America's Fastest Marathoner, Slows Down")

ph21_text

# 22. A Rainy Anniversary in Tahrir Square
ph22 <- read_html("https://www.newyorker.com/news/daily-comment/a-rainy-anniversary-in-tahrir-square")

ph22_text <- ph22 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "22") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "A Rainy Anniversary in Tahrir Square")

ph22_text

# 23. The Many Lives Along the Yangtze River
ph23 <- read_html("https://www.newyorker.com/culture/photo-booth/the-many-lives-along-the-yangtze-river")

ph23_text <- ph23 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "23") %>% 
  mutate( country = "China") %>% 
  mutate( title = "The Many Lives Along the Yangtze River")

ph23_text

# 24. Learning to Speak Lingerie
ph24 <- read_html("https://www.newyorker.com/magazine/2015/08/10/learning-to-speak-lingerie")

ph24_text <- ph24 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "24") %>% 
  mutate( country = "China") %>% 
  mutate( title = "Learning to Speak Lingerie")

ph24_text

# Travels with My Censor
ph25 <- read_html("https://www.newyorker.com/magazine/2015/03/09/travels-with-my-censor")

ph25_text <- ph25 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "25") %>% 
  mutate( country = "China") %>% 
  mutate( title = "Travels with My Censor")

ph25_text

# 26. Tales of the Trash
ph26 <- read_html("https://www.newyorker.com/magazine/2014/10/13/tales-trash")

ph26_text <- ph26 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "26") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "Tales of the Trash")

ph26_text

# 27. Fathers And Sons
ph27 <- read_html("https://www.newyorker.com/magazine/2014/06/09/election-day-4")

ph27_text <- ph27 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "27") %>% 
  mutate( country = "Uncategorized") %>% 
  mutate( title = "Fathers And Sons")

ph27_text

# 28. Revolution on Trial
ph28 <- read_html("https://www.newyorker.com/magazine/2014/03/10/revolution-on-trial")

ph28_text <- ph28 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "28") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "Revolution on Trial")

ph28_text

# 29. If Everyone Votes Yes, Is It Democracy?
ph29 <- read_html("https://www.newyorker.com/news/news-desk/if-everyone-votes-yes-is-it-democracy")

ph29_text <- ph29 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "29") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "If Everyone Votes Yes, Is It Democracy?")

ph29_text

# 30. The Buried
ph30 <- read_html("https://www.newyorker.com/magazine/2013/11/18/the-buried")

ph30_text <- ph30 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "30") %>%
  mutate( country = "Egypt") %>% 
  mutate( title = "The Buried")

ph30_text

# 31. Morsi's Chaotic Day in Court
ph31 <- read_html("https://www.newyorker.com/news/news-desk/morsis-chaotic-day-in-court")

ph31_text <- ph31 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "31") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "Morsi's Chaotic Day in Court")

ph31_text

# 32. Keeping the Faith
ph32 <- read_html("https://www.newyorker.com/magazine/2013/10/07/keeping-the-faith-2")

ph32_text <- ph32 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "32") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "Keeping the Faith")

ph32_text

# 33. Egypt Crosses the Line
ph33 <- read_html("https://www.newyorker.com/news/daily-comment/egypt-crosses-the-line")

ph33_text <- ph33 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "33") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "Egypt Crosses the Line")

ph33_text

# 34. The Showdown
ph34 <- read_html("https://www.newyorker.com/magazine/2013/07/22/the-showdown-2")

ph34_text <- ph34 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "34") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "The Showdown")

ph34_text

# 35. Morsi in Bazinga
ph35 <- read_html("https://www.newyorker.com/news/daily-comment/morsi-in-bazinga-jon-stewart-defends-bassem-youssef")

ph35_text <- ph35 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "35") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "Morsi in Bazinga")

ph35_text

# 36. Big Brothers
ph36 <- read_html("https://www.newyorker.com/magazine/2013/01/14/big-brothers")

ph36_text <- ph36 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "36") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "Big Brothers")

ph36_text

# 37. Brothers' Keepers
ph37 <- read_html("https://www.newyorker.com/magazine/2012/12/24/brothers-keepers")

ph37_text <- ph37 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "37") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "Brothers' Keepers")

ph37_text

# 38. Tahrir Square Turns Against Morsi
ph38 <- read_html("https://www.newyorker.com/news/news-desk/tahrir-square-turns-against-morsi")

ph38_text <- ph38 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "38") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "Tahrir Square Turns Against Morsi")

ph38_text

# 39. Cairo: Between the Protesters and the Embassy
ph39 <- read_html("https://www.newyorker.com/news/news-desk/cairo-between-the-protesters-and-the-embassy")

ph39_text <- ph39 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "39") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "Cairo: Between the Protesters and the Embassy")

ph39_text

# 40. Wasta
ph40 <- read_html("https://www.newyorker.com/magazine/2012/07/09/wasta")

ph40_text <- ph40 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "40") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "Wasta")

ph40_text

# 41. No Joy in Cairo
ph41 <- read_html("https://www.newyorker.com/news/news-desk/no-joy-in-cairo")

ph41_text <- ph41 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "41") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "No Joy in Cairo")

ph41_text

# 42. A Coup in Cairo?
ph42 <- read_html("https://www.newyorker.com/news/news-desk/a-coup-in-cairo")

ph42_text <- ph42 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "42") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "A Coup in Cairo?")

ph42_text

# 43. Arab Summer
ph43 <- read_html("https://www.newyorker.com/magazine/2012/06/18/arab-summer")

ph43_text <- ph43 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "43") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "Arab Summer")

ph43_text

# 44. Identity Parade
ph44 <- read_html("https://www.newyorker.com/magazine/2012/05/21/identity-parade")

ph44_text <- ph44 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "44") %>% 
  mutate( country = "Uncategorized") %>% 
  mutate( title = "Identity Parade")

ph44_text

# 45. All Due Respect
ph45 <- read_html("https://www.newyorker.com/magazine/2012/01/09/all-due-respect")

ph45_text <- ph45 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "45") %>% 
  mutate( country = "U.S.") %>% 
  mutate( title = "All Due Respect")

ph45_text

# 46. The Mosque on the Square
ph46 <- read_html("https://www.newyorker.com/magazine/2011/12/19/the-mosque-on-the-square")

ph46_text <- ph46 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "46") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "The Mosque on the Square")

ph46_text

# 47. Dr. Don
ph47 <- read_html("https://www.newyorker.com/magazine/2011/09/26/dr-don")

ph47_text <- ph47 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "47") %>% 
  mutate( country = "U.S.") %>% 
  mutate( title = "Dr. Don")

ph47_text

# 48. What Mortenson Got Wrong
ph48 <- read_html("https://www.newyorker.com/news/news-desk/what-mortenson-got-wrong")

ph48_text <- ph48 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "48") %>% 
  mutate( country = "Egypt") %>% 
  mutate( title = "What Mortenson Got Wrong")

ph48_text

# 49. Sargent Shriver, the Peace Corps, and Martin Luther King, Jr.
ph49 <- read_html("https://www.newyorker.com/news/news-desk/sargent-shriver-the-peace-corps-and-martin-luther-king-jr")

ph49_text <- ph49 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "49") %>% 
  mutate( country = "U.S.") %>% 
  mutate( title = "Sargent Shriver")

ph49_text

# 50. Village Voice
ph50 <- read_html("https://www.newyorker.com/magazine/2010/12/20/village-voice")

ph50_text <- ph50 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "50") %>% 
  mutate( country = "Uncategorized") %>% 
  mutate( title = "Village Voice")

ph50_text

# 51. The Uranium Widows
ph51 <- read_html("https://www.newyorker.com/magazine/2010/09/13/the-uranium-widows")

ph51_text <- ph51 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "51") %>% 
  mutate( country = "U.S.") %>% 
  mutate( title = "The Uranium Widows")

ph51_text

# 52. Go West
ph52 <- read_html("https://www.newyorker.com/magazine/2010/04/19/go-west")

ph52_text <- ph52 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "52") %>% 
  mutate( country = "U.S.") %>% 
  mutate( title = "Go West")

ph52_text

# 53. The Great Whatnot of China
ph53 <- read_html("https://www.newyorker.com/news/news-desk/the-great-whatnot-of-china")

ph53_text <- ph53 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "53") %>% 
  mutate( country = "China") %>% 
  mutate( title = "The Great Whatnot of China")

ph53_text

# 54. The Doorknob
ph54 <- read_html("https://www.newyorker.com/news/news-desk/the-doorknob")

ph54_text <- ph54 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "54") %>% 
  mutate( country = "Uncategorized") %>% 
  mutate( title = "The Doorknob")

ph54_text

# 55. Peter Hessler: Meb Keflezighi's Marathon Win
ph55 <- read_html("https://www.newyorker.com/news/news-desk/peter-hessler-meb-keflezighis-marathon-win")

ph55_text <- ph55 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "55") %>% 
  mutate( country = "U.S.") %>% 
  mutate( title = "Peter Hessler: Meb Keflezighi's Marathon Win")

ph55_text

# 56. Chinese Barbizon
ph56 <- read_html("https://www.newyorker.com/magazine/2009/10/26/chinese-barbizon")

ph56_text <- ph56 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "56") %>% 
  mutate( country = "China") %>% 
  mutate( title = "Chinese Barbizon")

ph56_text

# 57. Strange Stones
ph57 <- read_html("https://www.newyorker.com/magazine/2009/01/12/strange-stones")

ph57_text <- ph57 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "57") %>% 
  mutate( country = "China") %>% 
  mutate( title = "Strange Stones")

ph57_text

# 58. The Home Team
ph58 <- read_html("https://www.newyorker.com/magazine/2008/09/15/the-home-team")

ph58_text <- ph58 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "58") %>% 
  mutate( country = "China") %>% 
  mutate( title = "The Home Team")

ph58_text

# 59. Running To Beijing
ph59 <- read_html("https://www.newyorker.com/magazine/2008/08/11/running-to-beijing")

ph59_text <- ph59 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "59") %>% 
  mutate( country = "China") %>% 
  mutate( title = "Running To Beijing")

ph59_text

# 60. After the Earthquake
ph60 <- read_html("https://www.newyorker.com/magazine/2008/05/19/after-the-earthquake")

ph60_text <- ph60 %>% 
  html_elements(".paywall") %>% 
  html_text() %>% 
  unlist() %>% 
  tibble() %>% 
  mutate(Num = "60") %>% 
  mutate( country = "China") %>% 
  mutate( title = "After the Earthquake")

ph60_text
```


```{r}
# Combine the data
ph_text1 <- bind_rows(ph1_text,ph2_text,ph3_text,ph4_text,ph5_text,ph6_text,
                      ph7_text,ph8_text,ph9_text,ph10_text)
```

```{r include=FALSE}
ph_text2 <- bind_rows(ph11_text,ph12_text,ph13_text,ph14_text,ph15_text,
                      ph16_text,ph17_text,ph18_text,ph19_text,ph20_text)

ph_text3 <- bind_rows(ph21_text,ph22_text,ph23_text,ph24_text,ph25_text,
                      ph26_text,ph27_text,ph28_text,ph29_text,ph30_text)  

ph_text4 <- bind_rows(ph31_text,ph32_text,ph33_text,ph34_text,ph35_text,
                      ph36_text,ph37_text,ph38_text,ph39_text,ph40_text)

ph_text5 <- bind_rows(ph41_text,ph42_text,ph43_text,ph44_text,ph45_text,
                      ph46_text,ph47_text,ph48_text,ph49_text,ph50_text)

ph_text6 <- bind_rows(ph51_text,ph52_text,ph53_text,ph54_text,ph55_text,
                      ph56_text,ph57_text,ph58_text,ph59_text,ph60_text)
```

```{r}
# The final original dataset
ph_text <- bind_rows(ph_text1,ph_text2,ph_text3,ph_text4,ph_text5,ph_text6) %>%
  rename("text" = ".") 
```

## Data Analysis

### 1. Sentiment Analysis

Sentiment analysis is what interests me the most. What I would like to know is whether Peter's wording varies depending on the country he is describing.
The subjects of his articles can be broadly divided into four categories: China, Egypt, the United States, and some personal topics. I call this classification "country" and have conducted a sentiment analysis using the country classification.

```{r Sentiment}
# Create new stop words set based on the results
new_stops <- tibble(word =c("told","it's","didn't","don't",
                            "hundred","thousand","chen","zhang",
                            "luo","li","yakuza","rajeev","namje",
                            "mochizuki"))

full_stop <- stop_words %>% 
  bind_rows(new_stops)

# Clean the data
ph_text_1 <- ph_text %>% 
  unnest_tokens(input = text,
                 output = word) %>% 
  anti_join(full_stop) %>% 
  filter(!(gsub("'", "", word) %in% gsub("'", "", stop_words$word)) & word != "")

# Sentiment Analysis 1: Based on different countries
ph_text_1 %>% 
  left_join(sentiments) %>% 
  filter(!is.na(sentiment)) %>% 
  count(country,sentiment, sort = TRUE) %>% 
  ggplot() + 
  geom_col(aes(x = n, y = country,
               fill = sentiment),
               position = "fill")+
  ggtitle("Sentiment Analysis 1 \n Based on different countries")+
  ylab("Countries")
```


```{r}
# Sentiment Analysis 2: Based on both countries and articles
ph_text_1 %>% 
  inner_join(get_sentiments("bing")) %>%
  count(country,title,sentiment) %>%
  pivot_wider(names_from = sentiment,
              values_from = n) %>% 
  mutate(sent_score = positive - negative) %>% 
  ggplot() + 
  geom_col(aes(x = title, y = sent_score, 
               fill = country),
           show.legend = F) +
  facet_wrap(~country,scales = "free_x") +
  ggtitle("Sentiment Analysis 2 \n Based on both countries and articles")+
  xlab("Title")+
  ylab("Sent Scores")+
  theme(axis.text.x=element_blank())

```

#### Conclusion:

We can see that for all four classifications, Peter is actually more negative than positive. His views on China, the U.S. and the uncategorized are about the same, with slightly more negative descriptions about Egypt than the other classifications.
By analyzing the sentiment of the articles under each category, we can find that most of the articles under each category are negative. 

### 2. Word Cloud

After the sentiment analysis, I wanted to examine what specifics Peter's article was discussing in general. For this purpose, I created word clouds for all articles. The word cloud captures some of the most common words.

```{r warning=FALSE}
# Word Cloud
ph_text_1 %>% 
  count(word, sort = TRUE) %>% 
  with(wordcloud(word, n, max.words = 30, size = 0.6)) 
```

#### Conclusion:

In the word cloud we can see words like China, USA, Egypt, and some cities and people names, as expected.
Also, we can see that the most prominent word is people. This is in line with my survay of his writing style on the Internet, where many people think he is better at portraying people than big scenes.

### 3. Topic Model
I applied the topic model to examine the main themes of Peter's article. The following example uses 4 topic models, Beta matrix.

```{r}
# Topic Model - Beta
ph_dtm <- ph_text_1 %>% 
  count(country,word) %>% 
  cast_dtm(document = country, term = word,
           value = n)

ph_lda <- LDA(ph_dtm,k = 4,
                control = list(seed = 123))


ph_tidy <- tidy(ph_lda,matrix = "beta")

ph_top_terms1 <- ph_tidy %>% 
  group_by(topic) %>% 
  slice_max(beta,n = 15) %>% 
  ungroup() %>% 
  arrange(topic,-beta)%>% 
  mutate(topic = factor(topic)) %>% 
  mutate(topic = fct_recode(topic,
                            "U.S." = "1",
                            "China_City" = "2",
                            "China_Society" = "3",
                            "Egypt" = "4"))

ph_top_terms1 %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(beta, term, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  scale_y_reordered() +
  ggtitle("Topic Model - Beta")+
  xlab("Beta")+
  ylab("Term")

```

#### Conclusion:

As we can see, the models are mainly differentiated by country, not by topic, and it is difficult to differentiate between different topics in the same country. I tried 6 topic models and Gamma matrix, and the results were the same. Therefore, the topic model does not fit this dataset.

### 4. TF-IDF

After a failed attempt at topic model, I decided it would be better to discuss the content of Peter's article in categories. Using tf-idf, I sorted by country and looked at what was important in each category.
```{r}
# TF_IDF
# Bind tf_idf
ph_tf <- ph_text_1 %>% 
  count(word, country, sort = TRUE) %>% 
  bind_tf_idf(term = word,
              document = country,
              n=n)

ph_tf %>% 
  group_by(country) %>% 
  slice_max(tf_idf, n = 12) %>% 
  ungroup() %>%
  mutate(word = reorder(word,tf_idf)) %>% 
  ggplot() +
  geom_col(aes(x=tf_idf,y=word,fill=country), 
           show.legend = FALSE) +
  labs(x = "tf-idf", y = NULL) + 
  facet_wrap(~country, ncol = 2, scales = "free")+
  ggtitle("TF-IDF Analysis")
```

#### Conclusion:

I would say that tf-idf works well and makes sense. For China, Peter apparently had a lot of articles done after the epidemic started, so we can see key words like Wuhan, epidemic, lockdown, etc. For Egypt, there are a lot of names about the Arab Spring. For the US as well, there are a lot of important people mentioned, like Adelstein, also a journalist, Trump (we can see Denver is also an important word for him, wow).

### 5. Bigrams & Network Graph

Studying individual words has limitations in understanding the content, so I introduced bigram to analyze different countries.
```{r}
# Create bigrams
ph_text_2<- ph_text %>% 
  unnest_tokens(input = text,
                output = bigrams,
                token = "ngrams",
                n = 2)

# Count the bigrams
ph_count <- ph_text_2 %>% count(bigrams, sort = T)

# Separate into word1 and word2
bigram_counts <- ph_count %>% 
  separate(col = bigrams,
           into = c("word1","word2"),
           sep = " ") %>% 
  filter(!word1 %in% stop_words$word) %>% 
  filter(!word2 %in% stop_words$word) %>% 
  filter(!is.na(word1))

#Network graph
bigram_counts %>% 
  graph_from_data_frame()

set.seed(2022)

bigram_counts %>% 
  filter(n > 20) %>% 
  graph_from_data_frame() %>% 
  ggraph( layout = "fr") +
  geom_edge_link() +
  geom_node_point() +
  geom_node_text(aes(label = name), vjust = 1, hjust = 1)+
  ggtitle("Network Graph")
```

```{r}
# Separate bigrams
bigrams_separated <- ph_text_2 %>%
  separate(col = bigrams,
           into = c("word1", "word2"), 
           sep = " ")

# Remove Stop words
bigrams_filtered <- bigrams_separated %>%
  filter(!word1 %in% stop_words$word) %>%
  filter(!word2 %in% stop_words$word)

# Generate plot
bigrams_filtered %>% 
  unite(bigrams,word1,word2, sep = " ") %>% 
  count(country,bigrams, sort = TRUE) %>% 
  filter(bigrams != "NA NA") %>% 
  filter(n > 15) %>% 
  ggplot() + 
  geom_col(aes(x = n, y = bigrams,
               fill = country),show.legend = F) +
  facet_wrap(~country,scales = "free")+
  ggtitle("Bigram of different countries") +
  ylab("Bigrams")
```

#### Conclusion:

Bigram shows more content. For example, in China-related articles, Peter often mentions the communist party, Hong Kong, China's current chairman, and Sichuan University, the university he teaches at. In the article about Egypt, he mentions tear gas, security forces, human rights, etc., which are all related to Arab Spring. As for the US and uncategorized articles, the number of eligible Bigram is also limited because of the low number of articles.

## Conclusion

Based on the above analysis, the answer to our main question, "Is it true that Peter Hessler uses a more negative approach when writing about China" is clearly "No, it is not true." According to R's analysis, his statements are more negative than positive when describing all countries, but this is his writing style. Through tf-idf, bigrams, we learn some of the main contents of his article. For China, he has many articles discussing the pandemic. For Egypt, he focuses on the Arab Spring (I am not too familiar with the situation in Egypt, this is the conclusion from the keywords obtained through the search).
As a lover of literature, I'm not an avid fan of sentiment analysis because you often use negative terms but may be trying to convey a positive meaning. You must read through it and listen to how your heart sees the work. But for inexhaustible reading, like thousands, millions of tweets, or needing to make judgments in a short time, it's more efficient to let the machine tell you how to see it.












